\LaTeX\ Author Guidelines for \confName~Proceedings

### 2023-04-06 NTIRE 2023 Efficient SR Challenge Paper/PaperForReview.tex
x4 exp & x2 exp(未完成)
改好了

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{booktabs}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT 
\end{abstract}

@@

Introduction of efficient super resolution.

@@

Introduction of evaluation results.

@@

Conclusion.

>>>>

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{multicol}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
  Super-resolution techniques have become increasingly popular in recent years due to their ability to generate high-resolution images from low-resolution counterparts, which is an ill-posed problem in computer vision. Deep convolutional neural networks have shown exceptional performance in Single Image Super-Resolution (SISR), leading to the development of numerous deep learning-based methods. However, with mobile devices becoming a ubiquitous part of everyday life, there is a growing interest in developing Efficient Image Super-Resolution (EISR) methods that are computationally efficient and can produce high-quality images on mobile devices. This paper proposes a model-scaling based method to design an efficient model structure automatically. The "Expand Big, Then Shrink" method expands an old SOTA model to a new, larger dataset and then shrinks it, resulting in a more efficient model structure.
  % TODO: 补充一句实验结果 Our proposed method demonstrates improved performance in terms of FLOPs reduction and PSNR scores compared to state-of-the-art methods.
  The study's contributions include a discussion of how to design an efficient model in an automatic way, the proposed method to adapt an old SOTA model to a new, bigger dataset, and evaluation of the method on mainstream datasets.
\end{abstract}

@@

Single Image Super-Resolution (SISR) aims to reconstruct high-resolution images from their low-resolution counterparts, which is an ill-posed problem in computer vision. Over the years, deep convolutional neural networks have demonstrated remarkable performance in this domain, leading to the development of many deep learning-based methods. SISR has found widespread applications, including video gaming and video streaming, where high-resolution displays with high refresh rates are crucial. In particular, mobile devices have benefited from SISR techniques to enhance the user experience. However, mobile phones' power-constrained design with a limited power supply has made Efficient Image Super-Resolution (EISR) a topic of growing interest. Therefore, there is a need to explore EISR methods that are computationally efficient and can produce high-quality images on mobile devices.

@@

% TODO: 写一段结果
Introduction of evaluation results.

@@

This paper presents a method for Efficient Image Super-Resolution (EISR) that addresses the need for computationally efficient and high-quality image production on mobile devices. We proposed an automatic model-scaling method, "Expand Big, Then Shrink," which expands and then shrinks an old SOTA model to adapt to a new and bigger dataset. This work contributes to the ongoing efforts in developing efficient models for SISR, which is crucial in various fields, including video gaming, video streaming, and mobile devices. Our proposed method provides a promising direction for future research and applications of EISR.
